---
title: "R tutorial"
author: "Meng Cao"
date: "2/1/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\section{Try R as a calculator:}

1) 15 + 3

```{r calculator, echo=TRUE}
15 + 3
```

2) $\sqrt 4$

```{r, echo=TRUE}
sqrt(4)
```

3) $3 \times 15$

```{r, echo=TRUE}
3 * 15
```

4) $7/3$

```{r, echo=TRUE}
7/3
```

5) $4^2$
```{r, echo=TRUE}
4^2
```

\section{Binomial distribution with R:}
1) Help Binomial
```{r, echo=TRUE}
?Binomial
```

2) If $X\sim$ Bernoulli $(p = 0.5)$, calculate $P(X = 1)$.

Use the following R function:

dbinom(x, size, prob, log = FALSE)

x: value we are interested in (in this example 1)

size: n, number of Bernoulli trails (in this example 1)

prob: probability of $X = 1$

```{r, echo=TRUE}
dbinom(1, 1, 0.5)
```
3) If $X\sim$ Binomial $(n = 10, p = 0.5)$, calculate $P(X = 2)$.

```{r, echo=TRUE}
n = 10
x = 2
p = 0.5
dbinom(x, n, p)
choose(n, x) * (p)^x * (1 - p)^(n - x)
```

4) If $X\sim$ Binomial $(n = 10, p = 0.5)$, calculate $P(X \le 2)$.

Use the following R function:

dbinom(x, size, prob, log = FALSE)

x: value we are interested in (in this example 2)

size: n, number of Bernoulli trails (in this example 10)

prob: probability of $X = 2$

```{r, echo=TRUE}
n = 10
x = 2
p = 0.5
pbinom(x, n, p)

result = 0
for(ii in c(0:x)){
  result = result + choose(n, ii) * (p)^ii * (1 - p)^(n - ii)
}
result
```

5) Bolts Example in Lesson 8:

$X \sim \text{Binom}(n = 25, p = 0.05)$

a) $P(X = 2)$

```{r, echo=TRUE}
n = 25
x = 2
p = 0.05
dbinom(x, n, p)
```

b) $P(X \le 4)$

```{r, echo=TRUE}
n = 25
x = 4
p = 0.05
pbinom(x, n, p)
```

c) $P(X > 4)$

```{r, echo=TRUE}
n = 25
x = 4
p = 0.05
1 - pbinom(x, n, p)
```

d) $E[X] = n \times p$

```{r, echo=TRUE}
n = 25
p = 0.05
n*p
```


$SD(X) = \sqrt {n \times p \times (1-p)}$

```{r, echo=TRUE}
n = 25
p = 0.05
sqrt(n*p*(1-p))
```

6) Medication: $X \sim \text{Binom}(n = 12, p = 0.5)$

a) $P(X \ge 11)$
```{r, echo=TRUE}
n = 12
x = 10
p = 0.5
1 - pbinom(x, n, p)
```


b) No, it would be very unlikely to see this result for an ineffective medicine.














